### 2019-10-10 introduction.tex
midway through intro and letter

@@

Using this tabular layout effectively involves
navigation, \ie
{\em ``the process of viewing and manipulating the computer display to
show another portion of the information space''}~\cite{nav-study}.
Navigation is supported
via two unit operations, scrolling and steering.
\saj{Scrolling is the action of moving displayed text or graphics up, down, or across on a computer screen in order to view different parts of the spreadsheet.}
For example, when analyzing data, users may scroll
to compare data across different screens, or to get
a high-level view of the overall spreadsheet.
\saj{Steering, on the other hand, involves clicking the left mouse button and then dragging the mouse pointer through the spreadsheet to select a specific region.} For example, to issue a formula,
users may steer to select
the subset of the data
to be operated on as an argument within the formula.
Most frequently used spreadsheet formulae
require users to perform steering actions~\cite{bradbard2014spreadsheet, lawson2009comparison}.
Overall, both scrolling and steering are crucial as
users navigate spreadsheets to
identify, compare, and summarize data.

@@

However, navigating spreadsheet data using scrolling or steering
is often challenging, even for moderately sized spreadsheets that only span
a few screens~\cite{network-context,nardi1990spreadsheet}, due to multiple inter-related reasons:
\squishlist
\item {\em Loss of overview and context.}
When navigating
spreadsheets, users can easily lose the context
of where they are and where they should go next~\cite{network-context}.
The only navigational context provided by spreadsheets
is the built-in scrollbar that acts as a one-dimensional
overview and indicates the user's current location on the sheet.
However, since this overview does not capture the
layout and structure of the data,
users are forced to mentally assimilate
the layout and recall it on-demand, as they navigate a spreadsheet.

@@

Overall,  while navigating present-day spreadsheets, {\bf \em users often lose context,
get overwhelmed, and experience visual discontinuities.} 
Addressing these challenges requires considerable manual effort.
As we argue in Section~\ref{sec:related},
existing spreadsheet functionalities such as
pivot tables, named ranges, and subtotals,
while providing partial support for some of these challenges
(\eg pivot table generates a summary
while losing the mapping between the
raw data and the summary; named ranges requires users
to manually associate names with ranges of data),
do not eliminate them entirely.
With the ease of data generation, and with spreadsheets
now supporting data
of increasingly larger scales---\eg Google Sheets
now supports two million cells, a five-fold increase
from the previous limit of 400K cells---navigating
data within spreadsheets will become harder, not easier.

So, how do we support more effective navigation of data
within spreadsheets?
One approach would be to try to integrate
an overview of the overall structure of the data along
with the spreadsheet~\cite{grudin2001partitioning}.
The resulting integration would then be a classical
overview+detail interface
where the spreadsheet is the detailed view.
Overview+detail interfaces are used
to facilitate navigation in various domains such as 
text editors and maps~\cite{cockburn2009review},
and enable users to manipulate
the overview or detailed view,
to perform high-level or low-level operations,
respectively.
Overview+detail interfaces
have been shown to be effective in these domains,
reducing cognitive load for users by
providing the big picture first,
helping them quickly assimilate the information space~\cite{cockburn2009review}.
\saj{In this paper, our goal is to integrate an overview plug-in with spreadsheets that captures the overall structure of the data while allowing interactions that minimize the difficulties caused by typical navigational operations like scrolling and steering.}

>>>>

%!TEX root = main.tex

@@

Using this tabular layout effectively involves
navigation, \ie
{\em ``the process of viewing and manipulating the computer display to
show another portion of the information space''}~\cite{nav-study}.
Navigation is supported
via two unit operations, scrolling and steering.
\saj{Scrolling is the action of moving displayed text or graphics up, down, or across a computer screen, in order to view different parts of the spreadsheet.}
For example, when analyzing data, users may scroll
to compare data across different screens, or to get
a high-level view of the overall spreadsheet.
\saj{Steering, on the other hand, involves clicking the left mouse button and then dragging the mouse pointer through the spreadsheet to select a specific region.} For example, to issue a formula,
users may steer to select
the subset of the data
to be operated on as an argument within the formula.
Most frequently used spreadsheet formulae
require users to perform steering actions~\cite{bradbard2014spreadsheet, lawson2009comparison}.
Overall, both scrolling and steering are crucial as
users navigate spreadsheets to
identify, compare, and summarize data.

@@

\new{
However, navigating spreadsheets using scrolling or steering
is challenging, since spreadsheet data span multiple screens,
making it hard to synthesize, analyze, makes sense of, or
operate on it~\cite{network-context,nardi1990spreadsheet}.
With the ease of data generation, and with spreadsheets
now supporting increasingly larger datasets, \eg Google Sheets
now supports two million cells~\cite{}, a five-fold increase
from the previous limit of 400K cells, 
{\em navigating
data within spreadsheets is only becoming even harder},
thanks to
multiple inter-related reasons: 
}
\squishlist
\item {\em Loss of overview and context.}
When navigating
spreadsheets, users can easily lose the context
of where they are and where they should go next~\cite{network-context}.
The only navigational context provided by spreadsheets
is the built-in scrollbar that acts as a one-dimensional
overview and indicates the user's current location on the sheet.
However, since this overview does not capture the
layout and structure of the data,
users are forced to mentally assimilate
the layout and recall it on-demand, as they navigate a spreadsheet.

@@

\noindent
Overall,  while navigating present-day spreadsheets, 
{\bf \em users often lose context,
get overwhelmed, and experience visual discontinuities.} 
Addressing these challenges requires considerable manual effort.
As we \new{will} argue in Section~\ref{sec:related},
existing spreadsheet features such as
pivot tables, named ranges, and subtotals,
\new{partially alleviate 
some of the aforementioned 
challenges but do not eliminate them entirely.
For example, pivot tables generate a summary
while losing the correspondence between the
raw data and the summary, while named ranges require users
to manually associate names with ranges of data.}

So, how do we support more effective navigation of data
within spreadsheets?
One approach would be to try to integrate
an overview of the overall structure of the data along
with the spreadsheet~\cite{grudin2001partitioning}
\new{resulting in} a classical
overview+detail interface
where the spreadsheet is the detailed view.
Overview+detail interfaces are used
to facilitate navigation in various domains such as 
text editors and maps~\cite{cockburn2009review}.
\new{Users can manipulate
the overview or detailed view,
to perform high-level or low-level operations,
respectively.}
Overview+detail interfaces
have been shown to be effective in these domains,
reducing cognitive load for users by
providing \new{them} the big picture first,
helping them quickly assimilate 
the information space~\cite{cockburn2009review}.
\agp{got until here}
\saj{In this paper, our goal is to integrate an overview plug-in with spreadsheets that captures the overall structure of the data while allowing interactions that minimize the difficulties caused by typical navigational operations like scrolling and steering.}

### 2019-10-10 letter.tex
midway through intro and letter

The present version of the paper addresses all of the issues mentioned by the reviewers. The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 
\begin{itemize}
    \item More clearly articulate the merits over alternative tools, such as Keshif. 
     \item Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item Better justify the choice of tasks in the study. 
     \item Explain the choice of the four research questions.
     \item Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize} 
We have spent the last four months 
preparing a revised version of this paper.
\agp{One thing that is confusing is that the bulletpoints above
don't neatly map to the bulletpoints below, or the enumerated list after that.}
Here, we provide a response to the reviews. 
In our revised submission,
(i) we discuss the merits of having an interface like \noah
integrated within an existing spreadsheet, as opposed
to other general-purpose exploratory tools such as  Keshif;
(ii) we justify our design choice surrounding the binning mechanism;
and 
(iii) we enrich the user study design section further 
by providing justifications for comparing \noah and Excel, 
rephrasing our research questions reflecting the purpose of the user study, explaining the choice of quiz tasks,
(iv) we reorganize the results section to  highlight key contributions of \noah while explaining participant experiences in using the tool. Moreover, we report the  intra-participant differences for the study. 
The major changes to the paper include:

>>>>

The present version of the paper addresses all of the issues mentioned by the reviewers. The entire set of reviews are attached. In particular, the reviewers asked for the following changes for a revision: 
\begin{itemize}
    \item More clearly articulate the merits over alternative tools, such as Keshif. 
     \item Convincingly explain the design choice around the binning mechanism or revise
    that approach.
    \item Justify the choice of comparing with Excel and note the limitations of that
    approach.
     \item Better justify the choice of tasks in the study. 
     \item Explain the choice of the four research questions.
     \item Provide more details about the study, including reporting intra-participant
    differences.
\end{itemize} 
We have spent the last four months 
preparing a revised version of this paper.
\agp{One thing that is confusing is that the bulletpoints above
don't neatly map to the bulletpoints below, or the enumerated list after that. Stopped reading after this}
Here, we provide a response to the reviews. 
In our revised submission,
(i) we discuss the merits of having an interface like \noah
integrated within an existing spreadsheet, as opposed
to other general-purpose exploratory tools such as  Keshif;
(ii) we justify our design choice surrounding the binning mechanism;
and 
(iii) we enrich the user study design section further 
by providing justifications for comparing \noah and Excel, 
rephrasing our research questions reflecting the purpose of the user study, explaining the choice of quiz tasks,
(iv) we reorganize the results section to  highlight key contributions of \noah while explaining participant experiences in using the tool. Moreover, we report the  intra-participant differences for the study. 
The major changes to the paper include:
